%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\href{https://amadeus.com/}{Amadeus} - Payments} % Organization
    {Sophia-Antipolis, France} % Location
    {Feb. 2019 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design, Implement, Maintain payment security applications, specially within PCI-DSS standard scope.}
        \item {Automate CI/CD pipelines using Jenkins in a containerized environment (Docker).}
        \item {Create monitoring dashboards using Splunk, Prometheus, Grafana for application operability.}
        \item {Maintain and develop application hosting services for cryptographic operations relying on HSMs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\href{https://unicreditgroup.com/}{UniCredit} - Finantial risk} % Organization
    {Milan, Italy} % Location
    {May. 2015 - Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design, Implement, Maintain and Operate application responsible for bank counterparty credit risk computation.}
        \item {Optimize resources usage by leveraging on multiprocess/multithreaded distributed application.}
        \item {Build tooling for result analysis and application troubleshooting.}
        \item {Work in the frontline with the client to generate/collect requirements and handle the full application life-cycle.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher} % Job title
    {Undergraduate Research - Universidade de São Paulo} % Organization
    {São Paulo, Brazil} % Location
    {Mar. 2011 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research in fluid mechanics field.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
